Developing Measures of Public Perceptions of Values in Science

### 2022-06-08 talk/talk.qmd
as presented at VMST

---
title: "Developing Measures of Public Perceptions of Values in Science"
author: |
    | Dan Hicks 
    | Emilio Lobato
    | University of California, Merced
    | [`values-in-science-scale.netlify.app`](https://values-in-science-scale.netlify.app)
toc: false
toc-title: "Overview"
format: 
    revealjs:
        toc-depth: 1
        slide-number: true
        self-contained: true
        theme: [default, theming.scss]
link-citations: true
bibliography: ../paper/VISS.yaml
---

@@

- I'm a philosopher of science, STSer, data scientist
    - Science, values, and policy
    - Public scientific controversies
- Emilio is a cognitive psychologist
    - Conspiracy theories & other "epistemically unwarranted beliefs"
    - Relationship between prejudice and EUBs
</br>
- This project was funded out of my faculty startup funds at UC Merced

@@

- Qualitative designs to revise prompts
    - Paraphrase the prompt; think aloud
    - Likely will reduce measurement error
- Other endpoints
    - Dueling expert scenarios
    - Trust in science-policy institutions (EPA) rather than individual scientists [@BrownTrustExpertiseScientific2022]
    - Policy support

>>>>

---
title: "Developing Measures of Public Perceptions of Values in Science"
author: |
    | Dan Hicks 
    | Emilio Lobato
    | University of California, Merced
    | [`values-in-science-scale.netlify.app`](https://values-in-science-scale.netlify.app)
toc: false
toc-title: "Overview"
format: 
    revealjs:
        toc-depth: 1
        slide-number: true
        self-contained: true
        theme: [black, theming.scss]
link-citations: true
bibliography: ../paper/VISS.yaml
---

@@

- I'm a philosopher of science, STSer, data scientist
    - Science, values, and policy
    - Public scientific controversies
- Emilio is a cognitive psychologist
    - Conspiracy theories & other \
      "epistemically unwarranted beliefs"
    - Relationship between prejudice and EUBs
</br>
- This project was funded out of my faculty startup funds at UC Merced

@@

- Qualitative designs to revise prompts
    - Paraphrase the prompt; think aloud
    - Likely will reduce measurement error
- Other endpoints
    - Dueling expert scenarios
    - Trust in science-policy institutions (EPA) rather than individual scientists [@BrownTrustExpertiseScientific2022\; Biddle yesterday]
    - Policy support
